---
layout: post
category : tutorial
tagline: "Supporting tagline"
tags : [intro, tutorial, how-to, d3.js, brownian-motion]
---
{% include JB/setup %}
```{r include = FALSE, cache = FALSE}
chunk.label <- "2014-1-10-interactive-brownian"
opts_knit$set(base.url = "http://sachsmc.github.io/blog", unnamed.chunk.label = chunk.label)
fig.path <- "/assets/figures/"
opts_chunk$set(fig.path = fig.path)
opts_chunk$set(fig.cap = "center")
render_jekyll()
```

Creating Interactive Brownian Bridges using d3.js
========================================================

For my first post, I'd like to write a brief tutorial on how I made the cool interactive "Brownian Viaducts" as seen on my [homepage](http://sachsmc.github.io). There were a number of steps invovled in getting from the idea to the [d3](http://d3js.org) implementation that I plan to work through. But first, what is a Brownian Viaduct?

Brownian Bridges and Viaducts
-------------------------------------------------------
A [Brownian bridge](https://en.wikipedia.org/wiki/Brownian_bridge) is a Gaussian process indexed by (0, 1) that is pinned down to 0 at both ends. In statistics, Brownian bridges come up when we talk about the [empirical process](https://en.wikipedia.org/wiki/Empirical_process), that is the empirical cumulative distribution function (cdf). 

To solidify things, lets consider a sample from the Uniform distribution on (0, 1). The empirical cdf at _t_ is simply the proportion of samples that are less than _t_. 


```{r}
mean(runif(100) < .25)
```


Here I took _t_ = 0.25, but the empirical process is just the random function of _t_. Let's plot it:

```{r fig.width = 5, fig.height = 5}
empcdf.unif <- function(t){ 
  sapply(t, function(x) mean(runif(100) < x)) 
  }
curve(empcdf.unif, from = 0, to = 1)
```

